Resiliencia de *Quercus pyrenaica* a dos eventos de sequía

### 2018-01-18 pres/state_ms.Rmd
update state

---
title: "Resiliencia de *Quercus pyrenaica* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output: 
  beamer_presentation: 
    template: NULL 
    fig_caption: FALSE
    theme: metropolis
fontsize: 10pt
classoption: compress
bibliography: ../references.bib
csl: ../nature.csl
header-includes:
  \setbeamercolor{frametitle}{bg=gray}
  \hypersetup{colorlinks,citecolor=orange,filecolor=red,linkcolor=brown,urlcolor=blue}
---

>>>>

---
title: "Resiliencia de *Quercus pyrenaica* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output: 
  beamer_presentation: 
    template: NULL 
    fig_caption: FALSE
    theme: metropolis
fontsize: 10pt
classoption: compress
bibliography: ../refs/references.bib
csl: ../refs/nature.csl
header-includes:
  \setbeamercolor{frametitle}{bg=gray}
  \hypersetup{colorlinks,citecolor=orange,filecolor=red,linkcolor=brown,urlcolor=blue}
---
